Artificial Ecosystem Selection

### 2019-06-16 R/fluxes.Rmd
Work on modeling fluxes

# Convert ppm to umol
conc$ch4_umol <- conc$CH4_CONC * 0.965 / ((0.08206 * (293)))
conc

@@

```{r}

# Calculate fluxes from lm slopes
flux <- 
  conc %>% 
  group_by(Date, JAR) %>%
  do(tidy(lm(ch4_umol ~ days, data = .))) %>% 
  filter(term == 'days')#  %>% 
  select(Date, JAR, flux_umold = estimate)

flux <- 
  conc %>% 
  group_by(Date, JAR) %>%
  #do(tidy(glm(ch4_umol ~ days, data = ., family = gaussian(link = "log")))) %>% 
    nest() %>% 
mutate(fit_glm = purrr::map(data, ~ glm(ch4_umol ~ days, data = ., family = gaussian(link = "log"))),
         fit_lm = purrr::map(data, ~ lm(ch4_umol ~ days, data = .)))
flux %>% 
    mutate(aov = map2(fit_glm, fit_lm, stats::anova)) %>% 
    pull(aov)

out %>% 
    mutate(aov = map2(fit_nls, fit_lm, stats::anova)) %>% 
    pull(aov) %>% head(2)

>>>>

# Convert ppm to umol
conc$ch4_umol <- conc$CH4_CONC * 0.965 / ((0.08206 * (293)))

@@

```{r calc_flux}

## Calculate fluxes from lm slopes
#flux <- 
#  conc %>% 
#  group_by(Date, JAR) %>%
#  do(tidy(lm(ch4_umol ~ days, data = .))) %>% 
#  filter(term == 'days')#  %>% 
#  select(Date, JAR, flux_umold = estimate)
ggplot(conc[conc$Date == "20190614" & conc$JAR == 8,], aes(x = days, y = ch4_umol)) +
  geom_point() +
  stat_smooth(method = "glm", method.args = list(family = gaussian(link = "log")))
flux <- 
  conc %>% 
  group_by(transfer, Date, JAR, selected) %>%
  #do(tidy(glm(ch4_umol ~ days, data = ., family = gaussian(link = "log")))) %>% 
    nest() %>% 
mutate(fit_glm = purrr::map(data, ~ glm(ch4_umol ~ days, data = ., family = gaussian(link = "log"))),
         fit_lm = purrr::map(data, ~ lm(ch4_umol ~ days, data = .)))
results <-
flux %>% 
  mutate(glance_lm = map(fit_lm, glance),
         glance_glm = map(fit_glm, glance)) %>% 
        unnest(glance_lm, glance_glm) %>% 
        select(transfer, Date, JAR, fit_lm, fit_glm, deviance, deviance1) %>% 
        mutate(diff_deviance = deviance - deviance1) %>% 
        select(-deviance, -deviance1)
